---
title: "Netzer Report Tree Weight Formula"
author: "Bradford Bender"
date: "December 16, 2015"
output: slidy_presentation
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets
- Start Rstudio & set up Github & local repositories
- Start overview Slidy Markdown File to document process
- Load Required Packages
- Build Container Folder Structure for Sharing Analysis
- Use Rstudio Package Developer Build Tool for Package template container
- Enable the devtools and Roxygen features Build  
- Start Process

## Slide with R Code and Output

```{r}
# Installed Git located at C:\Program Files\Git\bin\git.exe
# set up Git repo https://github.com/2ndFloorStuff/NetzerTreeWeights.git
# started a project (Local Folder) C:\User|Brad\Dropbox|Rstudio\NetzerTreeWeights
# follow instructions at < https://support.rstudio.com/hc/en-us/articles/200532077-Version-Control-with-Git-and-SVN >
# 1.)The core software development utilities required for R package development can be obtained from the "Rtools**.exe"" download on CRAN: https://cran.rstudio.com/bin/windows/Rtools/.
# 2.) To build manuals and vignettes you'll also need to install the MikTeX LaTeX distribution for Windows which you can download from here: http://miktex.org/download.
#use the create.project() or package.skeleton()  function to start the project/package
#vignette("roxygen2",package="roxygen2")
#This is a change to test the Github repository pull request

summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

