---
title: "StartingWithSlidify"
author: "Bradford Bender"
date: "December 30, 2015"
output: ioslides_presentation
runtime: shiny
---

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Slide with Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Slide with Bullets

- 1 < http://slidify.org/start.html > Getting Started with Slidify
- 2 require(devtools)
- 2.1 install_github ("slidify","ramnathv")
- 2.2 install_github ("slidifyLibraries","ramnathv")
- 3.0 Library (slidify)
- 3.1 author("mydeck")
- 4.0 Write in RMarkdown, separating slides with a blank line followed by 3 dashes ---
- 5.0 slidify("index.Rmd")
- publish(user="USER",repo="REPO")
- Create empty repo on Github use your own github name and reponame

## Slide with R Code and Output

```{r}
summary(cars)
```


